Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-09-18 analysis/paper/sim_survey_paper.Rmd
Work to speed up the test_surveys loop and improve RAM management; use data.table::fwrite for export

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-09-04_test/test_output.RData")
```

>>>>

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-09-14_test/test_output.RData")
```
